\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-18 paper/main.tex
.

There are other types of indirect features that could be added to our
model. A common feature that may be added are drug indications which are
predictive of drug--target interactions \todo[inline]{CITE}\cite{}; however, we do
not include them in our model as including drug indications would
allow our model to make many trivial predictions based only on
remembering which targets are often used for which indication;
including network information would likely benefit predictions based
on drug indications because different drugs may target the same
pathway through different mechanisms.

Combining bottom-up and top-down approaches in a single model can
follow different strategies. Interaction networks are used widely to
determine indirect effects of molecular changes \todo[inline]{CITE}\cite{} and predict
drug--target interactions \todo[inline]{CITE}\cite{}. Our work relies on graph neural
networks as a way to combine qualitative information about
interactions with additional features (molecular interaction,
phenotypic and functional features); even if only some of these
features benefit from the information the graph provides, graph neural
networks will allow further extension of our model with additional
features in the future.

@@

One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work \cite{MolTrans2020}\cite{DeepConvDTI2019}, we find significant differences in predictive
performance across different splitting schemes.

>>>>

There are other types of indirect features that could be added to our
model. A common feature that may be added are drug indications which
are predictive of drug--target interactions \cite{Gottlieb2011};
however, we do not include them in our model as including drug
indications would allow our model to make many trivial predictions
based only on remembering which targets are often used for which
indication; including network information would likely benefit
predictions based on drug indications because different drugs may
target the same pathway through different mechanisms.

Combining bottom-up and top-down approaches in a single model can
follow different strategies. Interaction networks are used widely to
determine indirect effects of molecular changes and predict
drug--target interactions \cite{LotfiShahreza2017}. Our work relies on
graph neural networks as a way to combine qualitative information
about interactions with additional features (molecular interaction,
phenotypic and functional features); even if only some of these
features benefit from the information the graph provides, graph neural
networks will allow further extension of our model with additional
features in the future.

@@

One major component of our experiments was to determine how the
information that is available to a machine learning model during
training affects the performance of the model. Similarly to previous
work \cite{MolTrans2020, DeepConvDTI2019}, we find significant
differences in predictive performance across different splitting
schemes.
